% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[a4]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
%\usepackage[T1]{fontenc}
%\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{George Tyler}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{https://www.georgetyler.me/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, machine learning, econometrics, research assistant},
  pdftitle = {\name: George Tyler - CV},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

% Tagline
Masters student at LSE with skills in \textbf{economics, econometrics and data wrangling in Python, Stata, and R}; seeking roles in public policy macroeconomics. Australian/British dual citizen. 

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
%  \href{http://www.unc.edu/}{University of North Carolina} \\
  4 Chesterfield Road \\
  Newbury \\
  Berks, RG14 7QB
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Mobile: & +44 7500 949 112 \\
    Aus: &  +61 424 683 591 \\
    Email: & \href{mailto:george.tyler1998@gmail.com}{\tt george.tyler1998@gmail.com} \\
    %Homepage: & \href{http://www.georgetyler.me}{\tt http://www.georgetyler.me} \\
  \end{tabular}
\end{minipage}


%\section*{Personal}

%\begin{itemize}
%\item Born on September 29, 1895.
%\item United States Citizen.
%\end{itemize}


\section*{Education}
\subsubsection*{2021--2022: London School of Economics -- MSc Economics}

\subsubsection*{2017--2021: Durham University -- BA (Hons) Philosophy, Politics, and Economics}
First class honours. Dissertation: \textit{Risk Perception and Social Distancing: Evidence from 33 Million Tweets}.% Final year Economics modules: Advanced Macroeconomic Theory, Labour Economics. First class in all second year courses.%, \textbf{in the top 10 in cohort}. 
\subsubsection*{2019--2020: Ormond College, Melbourne University -- Study Abroad}
%Three honours courses: Mathematics for Economists, Econometrics 3, Development Economics. Other courses include Data Processing with Python (2nd-year CS course, including web-scraping and machine learning), 3rd-year Economic Analysis and Policy with Australian public policy focus. 
Honours economics courses and undergraduate CS courses. H1 degree award; Ormond Scholar.

\subsubsection*{2009--2016: The Oratory School, Woodcote, Oxfordshire}
A*AA at A level in Latin, Classical Greek, Mathematics respectively. 12 A*s at GCSE.
  
\section*{Experience}
\subsubsection*{Jun 2021 -- Aug 2021: Intern, Monetary Analysis, Bank of England}
I am in the Credit, Banking, and Finance team of the Monetary and Financial Conditions division. MFCD forms part of the Monetary Analysis directorate and conducts economic research to support the decisions of the Monetary Policy Comittee. I am completing a project on monetary policy transmission with a particular focus on mortgage rates.

\subsubsection*{Jun 2020 -- Aug 2020: Intern, Quantitative Risk Analytics, Bank of England}
I interned at the Bank of England, in a research team in the Financial Risk Management division of the Markets directorate. I completed two projects. In the first project I wrote and tested production code for a risk model; in the second, I researched and wrote a risk model for a new asset class. The research paper passed committee review and will be the basis of future work on the asset class for the QRA team; the code forms part of the Sterling Monetary Framework. 

\subsubsection*{Apr 2020 -- Jan 2021: Research Assistant, Faculty of Economics, Durham University}
I worked as a research assistant for Prof. Angel Hernando-Veciana on a paper about the public policy problems of COVID-19. I collected and cleaned large datasets in R, including webscraping scripting to generate panel data. Subsequently I was employed under Dr. Kenju Kamei in a lab experiment studying democracy norms.

\subsubsection*{Feb 2020 -- Jun 2020: Tutor, Quantitative Methods 1, Economics Faculty, Melbourne}
I worked as a TA in the first-year economic methods class, delivering tutorials to three classes per week, holding contact hours, and marking assessments. My method of conducting remote tutorials was recognised and I wrote a guide for student engagement over Zoom in the department remote-teaching handbook.

\subsubsection*{Dec 2019 -- Jan 2020: Intern, Programme Evaluation, Adara Group}
Worked on econometric evaluation of a neonatal health programme in rural Uganda at the head office of an NGO. I designed and implemented a cost-effectiveness analysis of Hospital to Home, a community neonatal healthcare program.

\subsubsection*{Oct 2018 -- Jun 2019: President, University College Boat Club}
Initially as Captain, I led a men’s squad of over 50 athletes. I stepped in as President during the second term, leading the executive team and managing the club’s significant capital assets. I oversaw a large year-on-year increase in enrolment and led two grant campaigns.

\subsubsection*{Jan -- Jul 2017: Future Hope, Kolkata, India}
Lived and worked in an education and health NGO for low-income children. I mentored and tutored a small group of young women each evening, and taught Mathematics, English, and Science to ages 8-14 during the school day. I led two large projects: a whole-school musical, and an initiative to teach basic music skills. 
\section*{Technical Skills}
\begin{itemize}
	\item Data science and Econometrics: assembling, cleaning, and modelling large (\(>50\)GB) datasets, using \texttt{R} and \texttt{Python}.
	\item Causal inference and related statistical techniques.
	\item Credit risk, asset pricing models. 
	\item Policy cost-effectiveness, particularly healthcare.
  \item Monetary policy analysis.
	\item \tt Python, R, Stata, Git, Unix.
\end{itemize}

\section*{Notable Achievements}
\begin{itemize}
	%\item \textbf{Currently co-authoring a health economics paper} with Adara Development on the `Hospital to Home' project.
	%\item \textbf{In the top 10 performers in my PPE cohort} at Durham University in the 2019 exams.
\item \textbf{Ormond Scholar} for 2019 and 2020, in recognition of outstanding academic achievement among Ormond residents.
\item \textbf{Awarded ``College Colours''} for 2018-19, a recognition of outstanding contribution to college life.
\item \textbf{Co-wrote and published a 50-page report} on the Durham Economics curriculum. Advocated for my findings on a panel with Cahal Moran, author of \textit{The Econocracy}.
\item \textbf{Led a 6-month project to produce The Lion King at Future Hope.} The production was at a large scale, involving all students, and made the Kolkata news.
\end{itemize}

%\section*{Other Positions of Responsibility}
%\begin{itemize}
%	\item Curriculum Officer, Durham Society for Economic Pluralism.% Further to publishing the Curriculum Report I managed a sub-committee, aiming at taking our findings to the national student body and achieving change within Durham Economics teaching.
%\item Editor-In-Chief, Durham University Economics Society Journal.

%\end{itemize}
%\section*{Publications}

%\subsection*{Journal Articles}

%\begin{itemize}
%\item A General Mathematical Theory of Depreciation, 1929, {\it Journal
%    of The American Statistical Association} 20, 340--353.
%\item Differential Equations Subject to Error, 1927, {\it Journal of The
%    American Statistical Association}.
%\item Applications of the Theory of Error to the Interpretation of
%  Trends (with H. Working), 1929, {\it Journal of the American
%    Statistical Association}.
%\end{itemize}

%\subsection*{Proceedings}

%\begin{itemize}
%\item A generalized T-Test and measure of multivariate dispersion,
%  Proc. Second Berkeley Symposium of Mathematical Statistics and
%  Probability, 1951.
%\end{itemize}

\bigskip

% Footer 
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}